Factors Influencing Early Childhood Comprehension of American English with a Bayesian Model

### 2024-12-04 paper/paper.qmd
update final paper

# CDI methodology overview and assessment

@@

## Survey implementation and Structure
To reach a diverse audience of caregivers, multiple distribution channels will be used. The link to the survey will be distributed via email invitations, community events, and targeted social media advertisements. The link to the survey is [here](https://forms.gle/2qVDdWk764dy16Jc6).

@@

1. Is your child between the ages of 8 and 36 months?\
* Yes / No\
2. Are you the primary caregiver of the child?\
* Yes / No\
3. Are you willing to provide information about your child’s language development?\
* Yes / No

@@

4. How old is your child?\
* 8-12 months / 13-24 months / 25-36 months\
5. What is your child's gender?\
* Boy / Girl / Prefer not to say\
6. What is your child’s race or ethnicity? (Other, please specify)\
* White / Black / African American / Hispanic or Latino / Asian / Other\
7. What is your highest level of education?(Other, please specify)\
* Primary / Secondary / Some College / Bachelor’s Degree / Graduate Degree / Other\
8. What is your current employment status? (Other, please specify)\
* Employed / Unemployed / Student / Homemaker/ Other\
9. What is your household income level?\
* Less than $30,000 / $30,000-$59,999 / $60,000-$99,999 / Greater than $100,000 / Prefer not to say\
10. How many language(s) do you speak at home?\
* Monolingual (One language) / Bilingual (Two languages) / Multilingual (Three or more languages)\

@@

11. At what age did your child start saying their first word?\
* 8-12 months / 13-24 months / 25-36 months\
12. How often does your child use words or phrases (like “mama”, “more”)?\
* Frequently (several times a day) / Occasionally (once or twice a day) / Rarely / Not yet\
13. Does your child use gestures (like waving, pointing) to communicate?\
* Yes, often / Occasionally / No\
14. How would you rate your child’s vocabulary comprehension?\
* Understands basic words (like names of family members) / Understands common household objects (like cup, ball) / Understands more complex phrases (like “Give me the red ball”) / Does not yet understand any words

@@

15. How often do you engage in activities that promote language development (like reading, or singing songs)?\
* Daily / Several times a week / Once a week or less / Never\
16. Do you use any of the following methods to support your child’s language development? (Check all that apply)\
* Reading books aloud / Singing songs / Playing interactive games (like peek-a-boo) / Speaking to the child in multiple languages / None of the above\
17. How often does your child interact with other children?\
* Frequently / Occasionally / Rarely / Does not interact with other children

@@

18. Do you believe there are any factors that have particularly influenced your child’s language development? (Such as: socioeconomic status, exposure to multiple languages, developmental disorders)\
* Yes / No\
19. Do you have any concerns about your child’s language development?\
* Yes / No

@@

20. Please select 'Agree' to verify that you are paying attention.\
* Agree / Disagree\
21. Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
* Yes / No

>>>>

# CDI methodology overview and improvement

@@

## Survey Implementation and Structure
To reach a diverse audience of caregivers, multiple distribution channels will be used. The link to the survey will be distributed via email invitations, community events, and targeted social media advertisements. The link to the survey is [here](https://forms.gle/2qVDdWk764dy16Jc6).

@@

1.Is your child between the ages of 8 and 36 months?

*Yes / No

2.Are you the primary caregiver of the child?

*Yes / No

3.Are you willing to provide information about your child’s language development?

*Yes / No

@@

4.How old is your child?

*8-12 months / 13-24 months / 25-36 months

5.What is your child's gender?

*Boy / Girl / Prefer not to say

6.What is your child’s race or ethnicity? (Other, please specify)

*White / Black / African American / Hispanic or Latino / Asian / Other

7.What is your highest level of education?(Other, please specify)

*Primary / Secondary / Some College / Bachelor’s Degree / Graduate Degree / Other

8.What is your current employment status? (Other, please specify)

*Employed / Unemployed / Student / Homemaker/ Other

9.What is your household income level?

*Less than $30,000 / $30,000-$59,999 / $60,000-$99,999 / Greater than $100,000 / Prefer not to say

10.How many language(s) do you speak at home?

*Monolingual (One language) / Bilingual (Two languages) / Multilingual (Three or more languages)

@@

11.At what age did your child start saying their first word?

*8-12 months / 13-24 months / 25-36 months

12.How often does your child use words or phrases (such as “mama”, “more”)?

*Frequently (several times a day) / Occasionally (once or twice a day) / Rarely / Not yet

13.Does your child use gestures (such as waving, pointing) to communicate?

*Yes, often / Occasionally / No

14.How would you rate your child’s vocabulary comprehension?

*Understands basic words (such as names of family members) / Understands common household objects (such as cup, ball) / Understands more complex phrases (such as “Give me the red ball”) / Does not yet understand any words

@@

15.How often do you engage in activities that promote language development (such as reading, or singing songs)?

*Daily / Several times a week / Once a week or less / Never

16.Do you use any of the following methods to support your child’s language development? (Check all that apply)

*Reading books aloud / Singing songs / Playing interactive games (such as peek-a-boo) / Speaking to the child in multiple languages / None of the above

17.How often does your child interact with other children?

*Frequently / Occasionally / Rarely / Does not interact with other children

@@

18.Do you believe there are any factors that have particularly influenced your child’s language development? (Such as: socioeconomic status, exposure to multiple languages, developmental disorders)

*Yes / No

19.Do you have any concerns about your child’s language development?

*Yes / No

@@

20.Please select 'Agree' to verify that you are paying attention.

*Agree / Disagree

21.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.

*Yes / No
